Something something

### 2024-08-30 paper/ms.tex
Update intro

\section{Introduction}\label{sec:intro}
For most elements, their stellar surface abundances retain the composition of their natal gas cloud. Therefore, the present-day distribution of stellar surface abundances encodes the chemical history of a galaxy. Two elements have received particular interest in the Milky Way: Fe and $\alpha$-elements (elements produced through the $\alpha$-process). Fe is produced in both Type Ia and Type II SNe whereas $\alpha$-elements are produced predominantly through Type II SNe. Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr for Type Ia), the ratio between $\alpha$-elements and Fe generally decreases with time.

This decline of \alphaFe{} over time has long been recognized \citep{1979ApJ...229.1046T}. This trend is only generally true, though, with non-monotonic behavior observed in observations and even one-zone chemical models \citep[e.g.][]{2022arXiv220402989C}.

Two types of supernovae (SNe) are responsible for most of the production of Fe and $\alpha$-elements: Type II and Type Ia \citep{2023A&ARv..31....1A}. Type II SNe originate from massive stars whose lifetimes are rather short (10s of Myr). Type Ia SNe, on the other hand, are thought to originate from white dwarfs whose masses have exceeded the Chandrasekar limit due to accretion from a donor star.

>>>>

\section{Introduction}\label{sec:intro}
For most elements, their stellar surface abundances retain the composition of their natal gas cloud. Therefore, the present-day distribution of stellar surface abundances encodes the chemical history of a galaxy. Two elements have received particular interest in the Milky Way: Fe and $\alpha$-elements (elements produced through the $\alpha$-process). Fe is produced in both Type Ia and Type II SNe whereas $\alpha$-elements are produced predominantly through Type II SNe. Because these SNe occur on different timescales (10s of Myr after star formation for Type II, as compared to 100s of Myr for Type Ia), the ratio between $\alpha$-elements and Fe is expected to generally decrease with time.

Because of their disparate formation channels, the two dimensional plane of \alphaFe{}-\FeH{} has received considerable interest. In the Milky Way, there is a well-established bimodality with separate high- and low-$\alpha$ sequences \citep{1996ASPC...92..307G,1998A&A...338..161F,2004AN....325....3F,2006MNRAS.367.1329R,2011A&A...535L..11A,2012A&A...545A..32A,2014A&A...562A..71B,2014ApJ...796...38N,2020MNRAS.493.2952H}. This bimodal distribution is shown in the upper left panel of Figure~\ref{fig:fig1}.

A more extensive survey of the different proposed formation mechanisms of this bimodality is given in \citet{2024arXiv240707985B}. Here, we mention simply that there are two approaches. First, the bimodality is a result of internal secular processes that generate the bimodality through radial migration \citep{2009MNRAS.396..203S,2021MNRAS.507.5882S,2023MNRAS.523.3791C} or clump formation \citep{2019MNRAS.484.3476C,2020MNRAS.492.4716B,2021MNRAS.502..260B,2023ApJ...953..128G}.

Second, the bimodality is generated through gas infall scenarios, either from specific gas accretion episodes from the intergalactic medium \citep{1997ApJ...477..765C,2009IAUS..254..191C,2017MNRAS.472.3637G,2019A&A...623A..60S}, or through a more self-consistent collapse sequence of the circumgalactic medium driven through feedback \citep{2021MNRAS.501.5176K}. Third and finally, the bimodality is generated through a merger process, either by enhancing the SFR of the Galaxy \citep{2004ApJ...612..894B,2005ApJ...630..298B,2007ApJ...658...60B,2010MNRAS.402.1489R} or by supplying a relatively pristine gas supply that resets the metallicity of the Galaxy \citep{2020MNRAS.491.5435B,2024MNRAS.528L.122C}. The fact that the Milky Way did undergo a merger with the Gaia-Sausage-Enceladus (GSE) satellite supports these scenarios \citep{2018MNRAS.478..611B,2018Natur.563...85H,2020ApJ...901...48N}.

In \citet{2024arXiv240707985B} we argued for an alternate formation scenario of the bimodality, for which we provide further support in this work. In this scenario, the bimodality is formed through a brief quiescent period in the Galaxy's history. During this period, which lasts $\sim300\,\Myr$, two things happen. First, as the chemical evolution of the galaxy proceeds fewer stars form. Second, because the SFR is lower, $\alpha$-element production drops and so the \alphaFe{} of the gas drops as well. The combination of these two effects is what leads to the valley in between the high- and low-$\alpha$ sequences.

In that work, we used idealized simulations of a galaxy merger that triggered a starburst which preceded the quiescent period. However, we argued that the merger aspect of that work was not necessary, but rather the quiescence. In this work, we study a subhalo from the Illustris TNG50 simulation which demonstrates this. This subhalo of interest (SoI) exhibits the sequence of events presented in \citet{2024arXiv240707985B} after a simple post-processing step which enhances the \alphaFe{} of old star particles. The SoI undergoes a brief quiescent period which neatly separates a high- and low-$\alpha$ sequence.

In Section~\ref{sec:methods} we discuss our selection technique which led to discovering the SoI, as well as a simple one zone chemical evolution model we use to justify our post-processing step. In Section~\ref{sec:results} we present the main results which we discuss and interpret in Section~\ref{sec:disc}. We conclude in Section~\ref{sec:conc}.

% This decline of \alphaFe{} over time has long been recognized \citep{1979ApJ...229.1046T}. This trend is only generally true, though, with non-monotonic behavior observed in observations and even one-zone chemical models \citep[e.g.][]{2022arXiv220402989C}.
